\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/figures.tex
Placement

\newcommand{\FigUpload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-up.pdf}
    \caption{\textbf{Upload Performance}\,---\, %
        We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
        As expected, TapDance's upload performance is several orders of magnitude lower than
        the link capacity, due to the overhead of frequent reconnects to the decoy.
    }
    \label{fig:upload}
\end{figure}
}

\newcommand{\FigDownload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-down.pdf}
    \caption{\textbf{Download Performance}\,---\, %
        Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
        While TapDance can achieve link capacity download, it still has to occasionally reconnect
        to the decoy, as seen by the periodic dips. These reconnects are more common the more data
        the client sends (e.g. requests or any upload data).
    }
    \label{fig:download}
\end{figure}
}

\newcommand{\FigTapBandwidth}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.90\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\, %
        We deployed our \scheme implementation in a realistic ISP testbed on a
        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}

>>>>

\newcommand{\FigUpload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}
    \caption{\textbf{Upload Performance}\,---\, %
        We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
        As expected, TapDance's upload performance is several orders of magnitude lower than
        the link capacity, due to the overhead of frequent reconnects to the decoy.
    }
    \label{fig:upload}
\end{figure}
}

\newcommand{\FigDownload}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}
    \caption{\textbf{Download Performance}\,---\, %
        Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
        While TapDance can achieve link capacity download, it still has to occasionally reconnect
        to the decoy, as seen by the periodic dips. These reconnects are more common the more data
        the client sends (e.g. requests or any upload data).
    }
    \label{fig:download}
\end{figure}
}

\newcommand{\FigTapBandwidth}{
\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
    \caption{\textbf{Tap Bandwidth}\,---\, %
        We deployed our \scheme implementation in a realistic ISP testbed on a
        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
        ranges from 2-17~Gbps.
    }
    \label{fig:tap-bandwidth}
\end{figure*}
}
